\TITLE

### 2023-06-16 paper/main.tex
update privacy according to Solove taxonomy

>>>>

According to Solove's Taxonomy of privacy~\cite{soloveTaxonomyPrivacy2006}, our protocol aims to prevent the following privacy risks:
\begin{itemize}
    \item Identification, linking of information to a particular individual;
    \item Secondary use, using personal information for a purpose other than the purpose it was collected; 
    \item Breach of confidentiality, breaking a promise to keep a person's information confidential;
    \item Disclosure, revealing truthful information about a person that impacts the ways others judge their character.
\end{itemize}
